---
title: "Assignment 1"
---

# Assignment 1

```{r}
1 + 1
```
# Assignment 1

My first assignment has two parts.

## (a) Video Summary

I watched the talk **“Veri Bilimi ve Endüstri Mühendisliği Üzerine Sohbetler - Baykal Hafızoğlu & Erdi Daşdemir.”**

In this talk, Baykal Hafızoğlu talks about his education and career journey. He graduated from Industrial Engineering at METU, completed his master’s degree, and then moved to the United States for his PhD at Arizona State University. After finishing his PhD, he started working in industry and continued his career in operations research, optimization, and analytics roles in different companies in the US.

One important point in the talk is that industrial engineering provides a strong background for analytics. He explains that the courses taken in industrial engineering, such as statistics, optimization, simulation, and data-related courses, are connected to descriptive, diagnostic, predictive, and prescriptive analytics. He also says that students should understand how these areas are related instead of seeing courses as separate subjects.

Another important message is that solving a model is not enough by itself. He emphasizes that analytical models should be delivered to end users in a usable way. According to him, deployment, user interface, early prototyping, and feedback from users are very important in real projects. He says that even a strong analytical model may fail if it cannot be explained well or used easily by people.

Overall, the talk shows that technical skills such as mathematical modeling, coding, and optimization are important, but communication, problem definition, and delivering practical solutions are also necessary for success in this field.

### Open-Ended Question

**Question:**  
According to Baykal Hafızoğlu, why is deployment as important as building a strong analytical or optimization model?

**Answer:**  
Because a model creates value only when end users can actually use it in practice. In the talk, he explains that many projects fail not because the model is weak, but because the solution is not delivered properly. Deployment, user interface, early prototypes, and user feedback are important because they help transform a technical model into a practical tool that people can use in real business settings.

### Multiple Choice Question

**Question:**  
Which of the following skills did Baykal Hafızoğlu especially recommend for students who want to work in optimization and operations research?

A) Only memorizing solver commands  
B) Mathematical modeling and coding skills  
C) Learning only visualization tools  
D) Focusing only on academic writing  

**Correct Answer:**  
**B) Mathematical modeling and coding skills**

---

## (b) Data Analysis with R

### Import the dataset

```{r}
library(dslabs)
data("polls_us_election_2016")

data <- polls_us_election_2016
```

### Define personal variables

```{r}
my_first <- "Oznur"
my_birth_year <- 2003
```

### Calculate k

```{r}
k <- (nchar(my_first) + my_birth_year) %% 15 + 8
k
```

### Display rows depending on k

```{r}
if (k %% 2 == 0) {
  selected_rows <- head(data, k)
} else {
  selected_rows <- tail(data, k)
}

selected_rows
```

### Count NA values

```{r}
total_na <- sum(is.na(data))
total_na
```

```{r}
na_per_column <- sort(colSums(is.na(data)), decreasing = TRUE)
head(na_per_column, 8)
```

### Replace NA values

```{r}
new_data <- data

numeric_cols <- sapply(new_data, is.numeric)

for (col in names(new_data)[numeric_cols]) {
  new_data[[col]][is.na(new_data[[col]])] <- my_birth_year + k
}
```

```{r}
char_factor_cols <- sapply(new_data, function(x) is.character(x) | is.factor(x))

for (col in names(new_data)[char_factor_cols]) {
  new_data[[col]] <- as.character(new_data[[col]])
  new_data[[col]][is.na(new_data[[col]])] <- paste0(my_first, "_", k)
}
```

### Display rows from new dataset

```{r}
if (k %% 2 == 0) {
  new_selected_rows <- head(new_data, k)
} else {
  new_selected_rows <- tail(new_data, k)
}

new_selected_rows
```

### Check remaining NA values

```{r}
sum(is.na(new_data))
```

```{r}
anyNA(new_data)
```